\documentclass{bilal}
\name{Bilal Abdul Halim}
\address{1234 Hill Street \\ Cookeville, TN 38501}
\address{(123)~$\cdot$~456~$\cdot$~7890 \\ Bilal.AbdulHalim@rockets.utoledo.edu}
\begin{document}
\bibliographystyle{abbrv}
\nobibliography{/home/xilal/Work/Citations/citations.bib}
\begin{rSection}{Education}
{\bf University of Toledo, Toledo, Ohio} \hfill {\em August 2020 -- May 2022} \\ 
Master's of Science in Mechanical Engineering \\
Overall GPA: 4.0

{\bf University of Toledo, Toledo, Ohio} \hfill {\em August 2015 -- May 2020} \\ 
Bachelor's of Science in Mechanical Engineering \\
Minor in Applied Mathematics \smallskip \\
Overall GPA: 3.9
\end{rSection}
\begin{rSection}{Experience}
    \begin{rSubsection}{Learning Enhancement Center}{October 2016 -- May 2020}{Engineering \& Mathematics Tutor}{Toledo, Ohio}
\item Tutored students individually and in groups all fundamental Mathematics and Engineering courses.
\item Guided students through complex mathematical and engineering problems.
\item Encouraged independent learning through different techniques.
\item Managed and trained new tutors on different skills and techniques.
\end{rSubsection}
\begin{rSubsection}{Plastic Technologies Inc}{January 2019 -- August 2019}{Finite Element Analysis Engineer}{Holland, Ohio}
\item Translated various physical problems to accurate FEA models.
\item Conducted stress and thermal analysis on different plastic packages.
\item Improved company's R\&D department through Abaqus Scripting (Python).
\item Worked closely with the design team providing suggestions based on FEA results.
\item Guided customers to an optimum package design through iterative FEA.
\item Wrote and organized proposals and reports for customers.
\end{rSubsection}
\begin{rSubsection}{PICSSL}{June 2017 -- January 2019}{Material Science Researcher}{Toledo, Ohio}
\item Lead a project on pressure-sensitive foams.
\item Conducted a plethora of polymer characterizations XRD, DSC, SEM, FTIR, UV VIS.
\item Designed and built a setup for in-situ pressure vs. transparency measurements, with a published patent.
\item Utilized Python and Excel to interpret data, generate high-quality charts and propose hypotheses.
\item Presented proposals and reports for specialized faculty members.
\end{rSubsection}
\end{rSection}
\begin{rSection}{Technical Skills}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
FEA \& CAD & Abaqus, SolidWorks, NX, Autocad \\
Software \& OS & Microsoft Office Suite, Linux, Vim \\
Computer Languages & Python, MATLAB, \LaTeX \\
\end{tabular}
\end{rSection}
%\begin{rSection}{Patents \& Publications}
%    \begin{list}{$\bigcdot$}{\leftmargin=0em}
%   \itemsep -0.5em 
%   \item \cite {}
%   \item \bibentry {}
%  \end{list}
%\end{rSection}
\end{document}
